### 2021-07-19 doc/thesis/chapters/deployment-on-hardware.tex
add some thoughts
\includepicture function with floating option; new block diagram
bd_impl_vivado diagram
structure sections

%%%%%%%%%%%%%%%%%%%%
\chapter{Deployment on Hardware}
\label{cha:DeploymentOnHardware}
  \section{Hardware Platform}
    \subsection{RTL2832u Dongle}
    \subsection{ZedBoard}

>>>>

%%%%%%%%%%%%%%%%%%%%
\chapter{Deployment on Hardware}
\label{cha:DeploymentOnHardware}

%%%%%%%%%%%%%%%%%%%%
\section{GNU Radio Transmitter}

%%%%%%%%%%%%%%%%%%%%
\section{Hardware Platform}
ZedBoard

%%%%%%%%%%%%%%%%%%%%
\subsection{RTL-SDR}
RTL2832U USB Dongle

%%%%%%%%%%%%%%%%%%%%
\section{Additional Implementation}

Chapter \ref{cha:Implementation} already described the development of the main IP.
In order to embed this IP on actual hardware, a significant additional amount of implementation is neccessary.
In this section, these additional parts of the implementation, which specifically enable and support the deployment on hardware, are described.

%%%%%%%%%%%%%%%%%%%%
\subsection{Block Diagram}

\includepicture [1.0] {Block diagram of the Vivado implementation.} {bd_impl_vivado} {img/draw.io/bd_impl_vivado}

%%%%%%%%%%%%%%%%%%%%
\subsection{Software}
